Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2021-09-13 paper/SupMat.Rnw
fixed curly bracket things in section 4

In fig \ref{fig:fig4} we plot IGR , $\Delta_i^{[E \nat C]$, and IGR $-\Delta_i^{[E \nat C]$ (see equation \ref{eq:decomp_overall_delta}) and the text below it.

From section \ref{sect:math_simplifications}, 
\begin{align}
\olr_{j \bs i} &= \E[\ln(1-\delta+E_j/C_{j \bs i})] \\
&= \E[\ln(1-\delta+\delta B_j/B_j)] \\
&= 0,
\end{align}
and
\begin{align}
\olep_j^{[E \nat C]} &= \E[r_j(E_j,C_{j \bs i})] - \E[r_j(E_j^\nat , C_{j \bs i}^\nat)] \\
&= \olr_{j \bs i} - \olr_{j \bs i}^\nat \\
&= 0. %\label{eq:decomp:j:EnatC}
\end{align}

Then $q_{ij}$ does not matter for IGR or $\Delta_i^{[E \nat C]$ because the second term in $\olr_{i \bs i}-q_{ij}\olr_{j \bs i}$ and $\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}$ are zero so 
\begin{equation}
\olr_{i \bs i}-q_{ij}\olr_{j \bs i}=\olr_{i \bs i}
\end{equation}
and 
\begin{equation}
\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}=\olep_i^{[E \nat C]}
\end{equation}

Similarly for IGR $-\Delta_i^{[E \nat C]$, 
\begin{equation}
(\olr_{i \bs i}-q_{ij}\olr_{j \bs i})-\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]} = \olr_{i \bs i}-\olep_i^{[E \nat C]}.
\end{equation}

Thus $q_{ij}$ does not matter for anything computed for Figure \ref{fig:fig4}.

>>>>

In fig \ref{MT-fig:fig4} we plot IGR , $\Delta_i^{[E \nat C]}$, and IGR $-\Delta_i^{[E \nat C]}$ (see equation \ref{eq:decomp_overall_delta}) and the text below it.  
From section \ref{sect:math_simplifications}, 
\begin{align}
\olr_{j \bs i} &= \E[\ln(1-\delta+E_j/C_{j \bs i})] \\
&= \E[\ln(1-\delta+\delta B_j/B_j)] \\
&= 0,
\end{align}
and
\begin{align}
\olep_j^{[E \nat C]} &= \E[r_j(E_j,C_{j \bs i})] - \E[r_j(E_j^\nat , C_{j \bs i}^\nat)] \\
&= \olr_{j \bs i} - \olr_{j \bs i}^\nat \\
&= 0. %\label{eq:decomp:j:EnatC}
\end{align}
Then $q_{ij}$ does not matter for IGR or $\Delta_i^{[E \nat C]}$ because the second term in $\olr_{i \bs i}-q_{ij}\olr_{j \bs i}$ and $\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}$ are zero so 
\begin{equation}
\olr_{i \bs i}-q_{ij}\olr_{j \bs i}=\olr_{i \bs i}
\end{equation}
and 
\begin{equation}
\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}=\olep_i^{[E \nat C]}
\end{equation}
Similarly for IGR $-\Delta_i^{[E \nat C]}$, 
\begin{equation}
(\olr_{i \bs i}-q_{ij}\olr_{j \bs i})-\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]} = \olr_{i \bs i}-\olep_i^{[E \nat C]}.
\end{equation}
Thus $q_{ij}$ does not matter for anything computed for Figure \ref{MT-fig:fig4}.
